Amazonian Narratives in Presidential Discourse (1985 to 2020)

### 2021-11-05 08112021_Sposito & Silva_Muller_DRAFT.Rmd
#tested knitting to pdf; needs formatting.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(stringi)
library(tm)
library(ggplot2)

@@

```{r setup, include=FALSE}
# Rename variables to adapt to text analysis packages' expectations
Amazon_speeches <- dplyr::rename(Amazon_speeches, fulltext = text, text = ccontext)

# Remove stop words and punctuation
Amazon_speeches$text <- tm::removePunctuation(Amazon_speeches$text)
Amazon_speeches$text <- tm::removeWords(Amazon_speeches$text,
                                        c(tm::stopwords("pt"), "nao", "amazonas",
                                          "amazonia", "governo", "amazonica", "ja", "aqui", "tambem",
                                          "no", "hoje", "presidente", "governador", "regiao", 
                                          "sao", "voces", "ser", "bem", "la", "so", "desta", "porque",
                                          "fazer", "quero", "ter", "vamos", "the", "of", "ha", "ai",
                                          "ate", "vai", "dizer", "estao", "it", "ver", "r", "	it",
                                          "cumprimentar", "gente", "estado", "querido", "queria",
                                          "todos", "brasil", "companheiro", "senhores",
                                          "companheiras", "companheiros", "companheira",
                                          "senhor", "senhora", "agora", "senhores", "senhoras", "caro",
                                          "grosso","ministro", "ministra", "josé", "pará", "acre", "roraima",
                                          "manaus", "rondônia", "ministros", "luiz", "antonio", "vou", "eduardo braga", "rio de janeiro",
                                          "sao paulo", "então", "pouco", "pode", "sul", "norte", "mato grosso",
                                          "outro", "onde", "discurso", "parte", "anos", "cada", "todo", "porto velho", "visite site",
                                          "site secretaria", "minas gerais", "lula silva", "inácio lula", "amapa", "bahia", "é",
                                          "lá", "et", "in"))

@@

```{r location, warning=FALSE, message=FALSE}
# Location was added with poldis::extraxt_location(), still needs to be improved...
# To see the variable summary, please run: `summary(as.factor(Amazon_speeches$location))`
# Let's code the Amazonian states, the other Brazilian states, and speeches delivered outside Brazil.
Amazon_lc <- mutate(Amazon_speeches, stage = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins|Maranhao", location) ~ "Amazonian_States", grepl("Alagoas|Bahia|Ceará|Distrito Federal|Goias|Minas Gerais|Espirito Santo|Paraiba|Parana|Pernambuco|Piaui|Rio de Janeiro|Rio Grande do Norte|Rio Grande do Sul|Santa Catarina|Sao Paulo|Brazil|Sergipe", location) ~ "Non_Amazonian_States", grepl("NA", location) ~ "Non_Identified", !grepl("Amazonian_States|Non_Amazonian_States|Non_Identified", location) ~ "International"))
summary(as.factor(Amazon_lc$stage)) # A lot of missing observations still ...
# Just a comparison with the proportion of speeches per stage on the broader dataset
stages <- mutate(BR_Presidential_Speeches, stage = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins|Maranhao", location) ~ "Amazonian States", grepl("Alagoas|Bahia|Ceará|Distrito Federal|Goias|Minas Gerais|Espirito Santo|Paraiba|Parana|Pernambuco|Piaui|Rio de Janeiro|Rio Grande do Norte|Rio Grande do Sul|Santa Catarina|Sao Paulo|Brazil|Sergipe", location) ~ "Non Amazonian States", grepl("NA", location) ~ "Non Identified", !grepl("Amazonian States|Non Amazonian States|Non Identified", location) ~ "International"))
stage_rate <- data.frame(Stage = names(summary(as.factor(Amazon_lc$stage))),
                         Amazon_speeches = paste0(round(as.numeric(summary(as.factor(Amazon_lc$stage))/861)*100, 2)," %"),
                         All_speeches = paste0(round(as.numeric(summary(as.factor(stages$stage))/6088)*100, 2)," %"))
stage_rate
```

@@

# Just plot in a wordcloud for words
set.seed(1234)
wordcloud(words = amazon_f$term, freq = amazon_f$freq, min.freq = 50,
          max.words=200, random.order = FALSE, rot.per=0.35, 
          colors = brewer.pal(8, "Dark2"))

@@

# A plot in a wordcloud for bigrams
set.seed(1234)
wordcloud(words = tamazon$bigram, freq = tamazon$n, min.freq = 20,
          max.words=200, random.order = FALSE, rot.per=0.35, 
          colors = brewer.pal(8, "Dark2"))

@@

```{r narratives, warning=FALSE, message=FALSE, echo=TRUE}
# Create the dictionary
sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|militar|fronteir|patrimonio|nacional|defesa|exercito")
development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|incentivos fiscais|integrar|integracao|zona franca|transamazonica|madeira|porto")
conservation <- ("preserv|conserv|determinacao|povos indigenas|indigenas|direitos humanos|areas demarcadas|queimada|sustentav|meio ambiente|florest")
anti_environmentalism <- ("preservamos demais|nao vamos demarcar|demarcar menos|agricultura|producao de gado|ambientalistas") # This appears harder to operationalize than others...
```

>>>>

```{r setup I, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(stringi)
library(tm)
library(ggplot2)
library(tidytext)
library(kableExtra)
library(stringr)
library(wordcloud)
library(RColorBrewer)

@@

```{r setup II, include=FALSE}
# Rename variables to adapt to text analysis packages' expectations
Amazon_speeches <- dplyr::rename(Amazon_speeches, fulltext = text, text = ccontext)

# Remove stop words and punctuation
Amazon_speeches$text <- tm::removePunctuation(Amazon_speeches$text)
Amazon_speeches$text <- tm::removeWords(Amazon_speeches$text,
                                        c(tm::stopwords("pt"), "nao", "amazonas",
                                          "amazonia", "governo", "amazonica", "ja", "aqui", "tambem",
                                          "no", "hoje", "presidente", "governador", "regiao", 
                                          "sao", "voces", "ser", "bem", "la", "so", "desta", "porque",
                                          "fazer", "quero", "ter", "vamos", "the", "of", "ha", "ai",
                                          "ate", "vai", "dizer", "estao", "it", "ver", "r", "	it",
                                          "cumprimentar", "gente", "estado", "querido", "queria",
                                          "todos", "brasil", "companheiro", "senhores",
                                          "companheiras", "companheiros", "companheira",
                                          "senhor", "senhora", "agora", "senhores", "senhoras", "caro",
                                          "grosso","ministro", "ministra", "josé", "pará", "acre", "roraima",
                                          "manaus", "rondônia", "ministros", "luiz", "antonio", "vou", "eduardo braga", "rio de janeiro",
                                          "rio grande do sul", "rio grande do norte", "sao paulo", "então", "pouco", "pode", "sul", "norte", "mato grosso",
                                          "outro", "onde", "discurso", "parte", "anos", "cada", "todo", "porto velho", "visite site",
                                          "site secretaria", "minas gerais", "lula silva", "inácio lula", "amapa", "bahia", "é",
                                          "lá", "et", "in"))

@@

```{r location, warning=FALSE, message=FALSE}
# Location was added with poldis::extraxt_location(), still needs to be improved...
# To see the variable summary, please run: `summary(as.factor(Amazon_speeches$location))`
# Let's code the Amazonian states, the other Brazilian states, and speeches delivered outside Brazil.
Amazon_lc <- mutate(Amazon_speeches, stage = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins|Maranhao", location) ~ "Amazonian_States", grepl("Alagoas|Bahia|Ceará|Distrito Federal|Goias|Minas Gerais|Espirito Santo|Paraiba|Parana|Pernambuco|Piaui|Rio de Janeiro|Rio Grande do Norte|Rio Grande do Sul|Santa Catarina|Sao Paulo|Brazil|Sergipe", location) ~ "Non_Amazonian_States", grepl("NA", location) ~ "Non_Identified", !grepl("Amazonian_States|Non_Amazonian_States|Non_Identified", location) ~ "International"))
# Just a comparison with the proportion of speeches per stage on the broader dataset
stages <- mutate(BR_Presidential_Speeches, stage = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins|Maranhao", location) ~ "Amazonian States", grepl("Alagoas|Bahia|Ceará|Distrito Federal|Goias|Minas Gerais|Espirito Santo|Paraiba|Parana|Pernambuco|Piaui|Rio de Janeiro|Rio Grande do Norte|Rio Grande do Sul|Santa Catarina|Sao Paulo|Brazil|Sergipe", location) ~ "Non Amazonian States", grepl("NA", location) ~ "Non Identified", !grepl("Amazonian States|Non Amazonian States|Non Identified", location) ~ "International"))
stage_rate <- data.frame(Stage = names(summary(as.factor(Amazon_lc$stage))),
                         Amazon_speeches = paste0(round(as.numeric(summary(as.factor(Amazon_lc$stage))/861)*100, 2)," %"),
                         All_speeches = paste0(round(as.numeric(summary(as.factor(stages$stage))/6088)*100, 2)," %"))
stage_rate
```

@@

@@

@@

```{r narratives dictionary, warning=FALSE, message=FALSE, echo=TRUE}

# Create the dictionary

sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|militar|fronteir|patrimonio|nacional|defesa|exercito|dono|nossa")
development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|incentivos fiscais|integrar|integracao|zona franca|transamazonica|madeira|porto")
conservation <- ("preserv|conserv|determinacao|povos indigenas|indigenas|direitos humanos|areas demarcadas|queimada|sustentav|meio ambiente|florest")
anti_environmentalism <- ("preservamos demais|nao vamos demarcar|demarcar menos|agricultura|producao de gado|ambientalistas") # This appears harder to operationalize than others...
